---
title: "Data QC"
author: "Heath O'Brien"
output:
  tufte::tufte_handout: default
  #tufte::tufte_html: default
---
<!-- see http://rstudio.github.io/tufte/ for info about tufte -->
<!-- type Rscript -e "library(rmarkdown); render('BamQC.rmd')" to knit to html on the server -->
```{r setup, include=FALSE}
knitr::opts_knit$set(echo = FALSE)
library(tidyverse)
library(stringr)
library(gridExtra)
library(tufte)
source("FormatGGplot.R")
RSeQCstats <- read_tsv("../Tables/read_numbers.txt", col_types = cols(sample = 'c'))
ReadNumbers <- select(RSeQCstats, sample, Unique)
RSeQCstats <- RSeQCstats %>% mutate(sample = str_extract(sample, "^[^-]+")) %>% group_by(sample) %>% summarise_each("sum")

```

# RSeQC
## Mapping Stats

`r margin_note("- Numbers of READS, which is 2x the number of sequenced fragments ")`
``` {r echo = FALSE}
#bam_stat.py
knitr::kable(
  bind_cols(RSeQCstats[,1], as.data.frame(sapply(RSeQCstats[,2:4], function(x) formatC(as.numeric(x), format='d', big.mark=','))))
)
```


## Distribution of Reads Among Features (proportion of tags mapping to different feature classes)
`r margin_note("- Intergenic only considers sequence within 10 kb upstream of TSS and downstream of TES")`
`r margin_note("- Looks like the GFF does not distinguish between CDS and UTR")`


``` {r echo = FALSE}
#read_distribution.py
RSeQCdistribution <- read_tsv("../Tables/read_distribution.txt", col_types = cols(sample = 'c'))
RSeQCdistribution <- dplyr::select(RSeQCstats, sample, Unique) %>% 
  full_join(RSeQCdistribution, by='sample') %>%
  mutate(tags_per_read=`Total Tags`/Unique) %>%
  dplyr::select(sample, tags_per_read, CDS, UTR, Intron, Intergenic)
knitr::kable(
  RSeQCdistribution
)


```

## Strand

`r margin_note("- Data consistent with unstranded experiment")`

```{r echo = FALSE}
RSeQCexpt <- read_tsv("../Tables/read_strand.txt", col_types = cols(sample = 'c'))

knitr::kable(
    RSeQCexpt
)

```

## Insert Size Distribution

`r margin_note("- Sharp peaks indicate that most fragments are shorter than the read length")`



```{r echo = FALSE, dev.args = list(bg = 'transparent')}
RSeQCdistance <- read_tsv("../Tables/read_distance.txt", col_types = cols(sample = 'c'))

ggplot(RSeQCdistance, aes(x=size, y=count, group=sample)) +
  geom_line() +
  ylab('reads') +
  xlab('inner distance') +
  scale_colour_brewer(type = "qual", palette = 6) +
  main_theme() +
  theme(legend.position=c(.8,.8))

```

## Splice Junction Saturation

`r margin_note("- Lots of unannotated genes")`

```{r warning=FALSE, echo = FALSE, dev.args = list(bg = 'transparent')}
RSeQCsat <- read_tsv("../Tables/junction_sat.txt", col_types = cols(sample = 'c'))
RSeQCsat <- RSeQCsat %>% mutate(BrainBankID=str_extract(sample, "^[^-]+")) %>%
  full_join(ReadNumbers) %>%
  dplyr::select(-BrainBankID)

ggplot(RSeQCsat, aes(y=junctions, x=Unique*percent_reads/100, group=sample)) +
  geom_point(size=.5) +
  #xlim(c(0,500)) +
  #scale_y_log10() +
  scale_colour_brewer(type = "qual", palette = 6) +
  main_theme() +
  theme(legend.position=c(.9,.9)) +
  facet_wrap(~ Category) +
  theme(axis.text.x=element_text(angle=-90)) +
  xlab("Number of Reads")
```
  
